Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-05-01 docs/00-manuscripts/ieee/ieee-manuscript.tex
harmonize xgboost names

	\acro{AGB}{above-ground biomass}
	\acro{ALE}{accumulated local effects}
	\acro{ALS}{airborn laser scanning}
	\acro{ANN}{artificial neural network}
	\acro{AUROC}{area under the receiver operating characteristics curve}
	\acro{BRT}{boosted regression trees}
	\acro{CART}{classification and regression trees}
	\acro{CNN}{convolutional neural networks}
	\acro{CV}{cross-validation}
	\acro{DAP}{digital aerial photogrammetry}
	\acro{ENM}{environmental niche modeling}
	\acro{FPR}{false positive rate}
	\acro{FFS}{forward feature selection}
	\acro{FS}{feature selection}
	\acro{GAM}{generalized additive model}
	\acro{GBM}{gradient boosting machine}
	\acro{GLM}{generalized linear model}
	\acro{ICGC}{Institut Cartografic I Geologic de Catalunya}
	\acro{IQR}{interquartile range}
	\acro{MARS}{multivariate adaptive regression splines}
	\acro{MBO}{model-based optimization}
	\acro{MEM}{maximum entropy model}
	\acro{ML}{machine learning}
	\acro{NDII}{normalized difference infrared index}
	\acro{NIR}{near-infrared}
	\acro{NRI}{normalized ratio index}
	\acro{OLS}{ordinary least squares}
	\acro{LiDAR}{light detection and ranging}
	\acro{LOWESS}{locally weighted scatter plot smoothing}
	\acro{PISR}{potential incoming solar radiation}
	\acro{PCA}{principal component analysis}
	\acro{PDP}{partial dependence plots}
	\acro{PLS}{partial least-squares}
	\acro{RBF}{radial basis function}
	\acro{RF}{random forest}
	\acro{RMSE}{root mean square error}
	\acro{RR}{ridge regression}
	\acro{RSS}{residual sum of squares}
	\acro{SAR}{synthetic aperture radar}
	\acro{SDM}{species distribution modeling}
	\acro{SMBO}{sequential-based model optimization}
	\acro{SVM}{support vector machine}
	\acro{TPR}{true positive rate}
	\acro{VI}{vegetation index}
	\acro{XGBOOST}{extreme gradient boosting}
\end{acronym}
\renewcommand{\IEEEiedlistdecl}{\relax}% reset back

@@

\begin{itemize}
	\item  Extreme Gradient Boosting (XGBOOST)
	\item  Random Forest (RF)
	\item  Penalized Regression (both L1 (lasso) and L2 (ridge))
	\item  Support Vector Machine (SVM)
\end{itemize}

\noindent \ac{RF} and {SVM} are well established algorithms that are widely used in environmental modeling.
\ac{XGBOOST} (commonly abbreviated as XGBOOST) showed promising results in benchmark competitions in recent years.
Penalized regression is a statistical modeling technique capable of dealing with highly-correlated covariates by applying a penalization term which shrinks the coefficients of the model\cite{hastie2001}.
Common penalties are 'lasso' (L1) and 'ridge' (L2).
The latter does not allow the full removal of variables from the model (penalization to zero) while the former does.
Both penalties can also be combined.
The combined approach is called 'elastic net' but was not used in this work.

@@

% - Ensemble FS shows no advantage to simple methods -> always one simple filter which is better. Ensemble filters are good across many different datasets
The models which used the Borda ensemble method in this study did not score better on average than models which used a single filter or no filter at all.
Ensemble methods have higher stability and robustness than single ones and have shown promising results in \cite{drotar2017a}.
Hence, their main advantage are stable performances across datasets with varying characteristics.
Certain single filter methods might yield better model performances for certain datasets but fail on others.
The fact that this study used multiple feature sets but only one dataset and tested many single filters could be a potential explanation why in almost all cases (besides XGBOOST on task HR-NRI-VI) a single filter outperformed the ensemble filter.
However, studies which used ensemble filters are still rare and usually these are not compared against single filters \cite{ghosh2019}.
Therefore no general statement can yet be made if the use of ensemble filters leads to a substantial better performance than applying one of the various single filter methods.
More case studies applying ensemble filter methods are needed.
We believe that ensemble filters can be a promising option in a machine-learning feature-selection portfolio.

>>>>

	\acro{AGB}{above-ground biomass}
	\acro{ALE}{accumulated local effects}
	\acro{ALS}{airborn laser scanning}
	\acro{ANN}{artificial neural network}
	\acro{AUROC}{area under the receiver operating characteristics curve}
	\acro{BRT}{boosted regression trees}
	\acro{CART}{classification and regression trees}
	\acro{CNN}{convolutional neural networks}
	\acro{CV}{cross-validation}
	\acro{DAP}{digital aerial photogrammetry}
	\acro{ENM}{environmental niche modeling}
	\acro{FPR}{false positive rate}
	\acro{FFS}{forward feature selection}
	\acro{FS}{feature selection}
	\acro{GAM}{generalized additive model}
	\acro{GBM}{gradient boosting machine}
	\acro{GLM}{generalized linear model}
	\acro{ICGC}{Institut Cartografic I Geologic de Catalunya}
	\acro{IQR}{interquartile range}
	\acro{MARS}{multivariate adaptive regression splines}
	\acro{MBO}{model-based optimization}
	\acro{MEM}{maximum entropy model}
	\acro{ML}{machine learning}
	\acro{NDII}{normalized difference infrared index}
	\acro{NIR}{near-infrared}
	\acro{NRI}{normalized ratio index}
	\acro{OLS}{ordinary least squares}
	\acro{LiDAR}{light detection and ranging}
	\acro{LOWESS}{locally weighted scatter plot smoothing}
	\acro{PISR}{potential incoming solar radiation}
	\acro{PCA}{principal component analysis}
	\acro{PDP}{partial dependence plots}
	\acro{PLS}{partial least-squares}
	\acro{RBF}{radial basis function}
	\acro{RF}{random forest}
	\acro{RMSE}{root mean square error}
	\acro{RR}{ridge regression}
	\acro{RSS}{residual sum of squares}
	\acro{SAR}{synthetic aperture radar}
	\acro{SDM}{species distribution modeling}
	\acro{SMBO}{sequential-based model optimization}
	\acro{SVM}{support vector machine}
	\acro{TPR}{true positive rate}
	\acro{VI}{vegetation index}
	\acro{XGBoost}{extreme gradient boosting}
\end{acronym}
\renewcommand{\IEEEiedlistdecl}{\relax}% reset back

@@

\begin{itemize}
	\item  Extreme Gradient Boosting (XGBoost)
	\item  Random Forest (RF)
	\item  Penalized Regression (both L1 (lasso) and L2 (ridge))
	\item  Support Vector Machine (SVM)
\end{itemize}

\noindent \ac{RF} and {SVM} are well established algorithms that are widely used in environmental modeling.
\ac{XGBoost} (commonly abbreviated as XGBoost) showed promising results in benchmark competitions in recent years.
Penalized regression is a statistical modeling technique capable of dealing with highly-correlated covariates by applying a penalization term which shrinks the coefficients of the model\cite{hastie2001}.
Common penalties are 'lasso' (L1) and 'ridge' (L2).
The latter does not allow the full removal of variables from the model (penalization to zero) while the former does.
Both penalties can also be combined.
The combined approach is called 'elastic net' but was not used in this work.

@@

% - Ensemble FS shows no advantage to simple methods -> always one simple filter which is better. Ensemble filters are good across many different datasets
The models which used the Borda ensemble method in this study did not score better on average than models which used a single filter or no filter at all.
Ensemble methods have higher stability and robustness than single ones and have shown promising results in \cite{drotar2017a}.
Hence, their main advantage are stable performances across datasets with varying characteristics.
Certain single filter methods might yield better model performances for certain datasets but fail on others.
The fact that this study used multiple feature sets but only one dataset and tested many single filters could be a potential explanation why in almost all cases (besides XGBoost on task HR-NRI-VI) a single filter outperformed the ensemble filter.
However, studies which used ensemble filters are still rare and usually these are not compared against single filters \cite{ghosh2019}.
Therefore no general statement can yet be made if the use of ensemble filters leads to a substantial better performance than applying one of the various single filter methods.
More case studies applying ensemble filter methods are needed.
We believe that ensemble filters can be a promising option in a machine-learning feature-selection portfolio.
